Hierarchical Time Series Forecasting in Emergency Medical Services

### 2022-11-22 manuscript/05-results.qmd
typos

@tbl-result-3 presents the accuracy of the forecast distributions measures by CRPS, which considers both forecasting reliability and interval sharpness. The smaller the value of CRPS, the better the comprehensive performance. We observe that forecast reconciliation results in forecast improvement for the total and health board level. CRPS is almost identical at the control area and health board levels. Base forecasts are slightly better at the control area level, while reconciliation is marginally accurate than base at the bottom level. The ensemble method is also more accurate for higher levels, but ETS performs well at the bottom level. @tbl-result-3 indicates that it generates accurate *distributional* forecasts. The marginal improvement in the average probabilistic forecast accuracy at the bottom level might be due to the reconciliation method giving improved forecast accuracy in the tails of the forecast distribution, which are critical for managing risks.

>>>>

@tbl-result-3 presents the accuracy of the forecast distributions measures by CRPS, which considers both forecasting reliability and interval sharpness. The smaller the value of CRPS, the better the comprehensive performance. We observe that forecast reconciliation results in forecast improvement for the total and health board level. CRPS is almost identical at the control area and botom levels. Base forecasts are slightly better at the control area level, while reconciliation is marginally accurate than base at the bottom level. The ensemble method is also more accurate for higher levels, but ETS performs well at the bottom level. @tbl-result-3 indicates that reconciliation using Mint  generates accurate *distributional* forecasts. The marginal improvement in the average probabilistic forecast accuracy at the bottom level might be due to the reconciliation method giving improved forecast accuracy in the tails of the forecast distribution, which are critical for managing risks.
